Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Versions changes to create the latent space grid

>>>>

We now compose the plot in the latent space. Apart from the item representation,
we need to plot the grid that corresponds to the latent space instead of the
test space.

```{r compose-oblique-plot-latent-space}
TAN_LS <- -CORR_VALUE / CORR_ARC_SIN

plot_oblique <- items_oblique |>
  arrange(desc(item))         |> # To plot them in reverse order
  ggplot(
    aes(
      origin_transf_1, origin_transf_2,
      xend  = end_transf_1, yend = end_transf_2,
      color = item, fill = item
    ),
  )                                                   +
  scale_x_continuous(
    limits       = c(-2, 3),
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  )                                                   +
  scale_y_continuous(
    limits       = c(-2, 2.8),
    breaks       = -3:3 * 2 * TAN_LS,
    labels       = function(y) 1 + y / (2 * TAN_LS),
    minor_breaks = 0,
    name         = NULL,
    oob          = oob_keep
  )                                                   +
  coord_fixed(expand = FALSE, clip = "on")            +
  scale_color_manual(values = PALETTE)                +
  geom_abline(slope = TAN_LS, linewidth = LINE_WIDTH) +
  geom_abline(
    slope     =  TAN_LS,
    intercept = -3:3 * 2 * TAN_LS,
    linewidth = LINE_WIDTH,
    linetype  = "17"
  )                                                         +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH)  +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  )                                                         +
  theme(
    axis.line          = element_blank(),
    panel.grid.major.x = element_line(
      color     = "black",
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```

```{r item-plot-latent-space-out}
#| fig.cap: |
#|   Item plots in an oblique, orthonormal latent space (with correlation = .5)
plot_oblique
```
